Draft Final Project

### 2020-04-30 Draft-Report.Rmd
adding stuff

>>>>

```{r}
model_1 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + positive + percent_white +State, #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)

model_2 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + positive + percent_white + (1 | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)

model_3<- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + positive + percent_white + (Day | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```
